A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-04-24 ms.tex
moved lots of text around to try to get a better organization

@@

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
at southern declinations ($\delta<-20$\arcdeg) (XXX cite).
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles for achieving the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization (XXX cite).
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 20\% or higher
% XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
\citep{Jacobs:2013p9713}, approximately matching the level of uncertainty in the catalogs.

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range XXX to XXX that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX document map
In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental
setup, observations and analysis method followed. In \S\ref{sec:fits} we
compare the spectra with available data.  We conclude in 
\S\ref{sec:Conclusion}.

@@

@@

% XXX write this section

However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
particularly at southern declinations ($\delta<-20$\arcdeg).

PAPER, in its maximum redundancy configuration, has a very broad beam with
% XXX need background on minimum/maximum array configurations
large regular grating side-lobes and is therefore limited to using the few
sources above $\sim$50 Jy for flux calibration. The best calibrator for most
% XXX qualify "best"
observations is Pictor A. For this source the current best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.

A method for decoupling uncertain fluxes from the uncertain beam has been
described by \citet{Pober:2012p8800}. In simulation the method was able to
achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
number of antennae and other variables. The Pober method emphasized the need
for many repeated measurements of each alt-az pointing. Further investigation
is under way to improve and implement this method and would be greatly aided by
the availability of precise flux measurements unaffected by primary beam
uncertainty. This paper reports a set of flux measurements where a primary beam
model has not been used to estimate the flux, but instead are directly
calibrated to a single calibrator making the track through the beam.

The spectra were measured by PAPER, a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). Since November 2011 it has been arranged in a maximally redundant grid configuration to make deep power spectral integrations \citep{Parsons:2012a}.
\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
% XXX add brief summary of observations.
}\label{fig:antpos}
\end{figure*}

In this paper our primary goal is to provide a subset of accurate fluxes
suitable for EoR power spectrum and catalog calibration.  After recording the
data used in this paper, PAPER was reconfigured into a redundant layout
optimized to detect a small number of power spectrum bins at high precision, an
arrangement which trades imaging dynamic range for power spectrum sensitivity.
As such it is only able to easily distinguish the very brightest sources on the
sky a step necessary for setting the overall flux scale \citep{Parsons2013b}. Of these, Pictor A is
one of the most useful, being bright, minimally resolved and far from from
confusing structure.

The data  include new measurements of Pictor A that are uncertain to 3.5\%,
close to the level of the most precise higher frequency measurements by
\citet{Wills:1975p9314}. Using these new measurements we update the spectral
calibration model to an accuracy of 2.5\%. As validation of this method, we
also measure a selection of 58 additional sources at the same Declination.  The
primary beam is calibrated using a single common source (J2331-416), thus
limiting the declination probed to $-45 \pm 5$\arcdeg.  The flux scale is set
by Monte Carlo fitting to a subset of sources, all of which are calibrated to
the Baars et al scale. 
%This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.

% XXX incorporate
%Given these shortcomings in the literature, we felt it prudent to examine-Pictor A directly.  We use data observed on JD2455747 
%from a 64-antenna single-polarization deployment of the 
%PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
%of these observations and their calibration are given in \citet{pober_et_al2013}.  In order to ensure that 
%errors in
%the beam model did not skew our result, we chose a set of calibrator sources near in declination
%to Pictor A that would follow nearly identical tracks through the primary beam.

% XXX incorporate
%To measure the spectrum of each source, we apply per-antenna phase and gain cal
%brations established-via self-calibration and remove
%the known dependence of amplifier gain and cable attenuation on ambient temperature was corrected
%using measured temperature data and temperature coefficients that were characterized in
%laboratory measurements \citep{parashare_bradley2009} and confirmed in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
%osition
%and sum over 
%all baselines greater than 20 wavelengths in length.
%A fringe-rate filter is applied to the resulting
%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
%$\pm$0.1 mHz from the fringe rate of the source in question.

% XXX incorporate
%To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
%weights derived from a model of
%PAPER's primary beam response as an effective approximation of inverse-variance weighting
%\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
%represents a best estimate given the limitations of the beam model and flux calibration that were established
%up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
%smoothed on 10-MHz scales,
%that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum of
%$S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ that represents the best fit to measurements below 1 GHz.
%This additional gain factor was applied to all measured spectra, including that
%of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
%through the PAPER beam, any errors present in the original measured spectra as a result of differences between
%the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
%should be corrected by the applied gain factor.

% XXX incorporate
%Finally, because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
%use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
%resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
%the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.

 \section{Observations and Data Reduction}
 \label{sec:Observations}

 Measurements are derived from observations using  the east-west dipole arms of
64 PAPER antennas deployed in the Karoo Radio Observatory site in South Africa
(see Figure \ref{fig:antpos}).  A 100-MHz band from 100-200MHz was correlated
with 2048 frequency channels and integrated for 10.7 seconds before
visibilities were stored.  Observations included here on  July 4, 2011, running
from JD2455748.17 to JD2455748.72. and October 17, 2011 running from
JD2455852.2 to JD2455852.6.  In both seasons two antennas were omitted owing to
malfunctioning signal path. This 20 hour long combined dataset provides
observations provides complete hour angle coverage for the entire 24 hours of
Right Ascension. The July portion of the dataset comes from the same observing
campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
%July (\#40,\#55), September (\#7,\#28)

@@

%CALIBRATION
\textbf{Antenna calibration}\\

% XXX time-dependent calibration is critical.  modify paragraph below
Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
Finally, measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was drived using coefficients characterized in
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

Antennae delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013XXX} and \citet{Stefan:2013:XXX}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

% XXX differentiate amp cal here from spectral cal that comes later.

%BEAMFORMING,FILTERING, AVERAGING
\textbf{Source Selection}\\

In order to ensure that errors in
the beam model did not skew our result, we chose a set of sources near in declination
to Pictor A that would follow nearly identical tracks through the primary beam.
A list of these 
sources is given in Table \ref{tab:src_spec}, with the spectra measure by PAPER
illustrated in Figure \ref{fig:src_spec}.  These sources were chosen on the basis of brightness and
proximity in declination to Pictor A.
% XXX merge this with paragraph below

@@

@@

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
% XXX clarify why one source used here, and more sources later 
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

@@

To compare with observations at other frequencies we must assume a spectral
model. The prevailing spectral model for low frequency radio sources is a
single power law due to synchrotron emission, though curvature or other
deviation from a power-law is not-uncommon.   To establish a baseline model, we
fit a spectral model to prior catalog data from the spectrally and spatially
cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method
described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for
these fits are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}.

@@

>>>>

\section{Introduction}

@@

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg (XXX cite).
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles for achieving the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization (XXX cite).
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 20\% or higher
% XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
\citep{Jacobs:2013p9713}, approximately matching the current level of uncertainty in catalogs.

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range XXX to XXX that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX update document map
In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental
setup, observations and analysis method followed. In \S\ref{sec:fits} we
compare the spectra with available data.  We conclude in 
\S\ref{sec:Conclusion}.

@@

\section{Background}

% XXX unsure about this section.  need someplace to give overviews of catalogs

% XXX elaborate on:
%However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
%particularly at southern declinations ($\delta<-20$\arcdeg).

% XXX remove PAPER specificity from below?
For power-spectrum measurements, PAPER uses an antenna layout
optimized to detect a small number of Fourier modes at high precision.  This ``maximum-redundancy''
array configuration trades imaging dynamic range for power spectrum sensitivity \citep{Parsons2012a}.
As such it is only able to easily distinguish the very brightest sources on the
sky for setting the overall flux scale \citep{Parsons2013b}. 
Of these, Pictor A is
one of the most useful, being bright, minimally resolved, and far from
confusing structure. 
For this source the current best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.
% XXX more background on pictor A

% XXX transition to the PAPER instrument
Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012a}.
% XXX to calibrate these observations...

A method for decoupling uncertain fluxes from the uncertain beam has been
described by \citet{Pober:2012p8800}. In simulation the method was able to
achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
number of antennae and other variables. The Pober method emphasized the need
for many repeated measurements of each alt-az pointing. Further investigation
is under way to improve and implement this method and would be greatly aided by
the availability of precise flux measurements unaffected by primary beam
uncertainty.

This paper reports a set of flux measurements where a primary beam
model has not been used to estimate the flux, but instead are directly
calibrated to a single calibrator making the track through the beam.

@@

% XXX incorporate
Given the shortcomings in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.

In order to ensure that 
errors in
the beam model did not skew our result, we chose a set of calibrator sources near in declination
to Pictor A that would follow nearly identical tracks through the primary beam.
This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.

In order to ensure that errors in
the beam model did not skew our result, we chose a set of sources near in declination
to Pictor A that would follow nearly identical tracks through the primary beam.
A list of these 
sources is given in Table \ref{tab:src_spec}. 
These sources were chosen on the basis of brightness and
proximity in declination to Pictor A.
% XXX specific declination range
% XXX merge this with paragraph below

% XXX equation for time-dependent beam amplitude times source flux for perceived flux density

To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
weights derived from a model of
PAPER's primary beam response as an effective approximation of inverse-variance weighting
\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
represents a best estimate given the limitations of the beam model and flux calibration that were established
up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
smoothed on 10-MHz scales,
that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
that represents the best fit to measurements below 1 GHz.
This additional gain factor was applied to all measured spectra, including that
of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
through the PAPER beam, any errors present in the original measured spectra as a result of differences between
the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
should be corrected by the applied gain factor.

Finally,
the flux scale is set
by Monte Carlo fitting to a subset of sources, all of which are calibrated to
the Baars et al scale. 
% XXX elaborate on this, more on Baars, less on MC

 \section{Data Reduction}
 \label{sec:Observations}

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
% XXX add brief summary of observations.
}\label{fig:antpos}
\end{figure*}

 Measurements are derived from observations using  the east-west dipole arms of
64 PAPER antennas deployed in a minimum-redundancy imaging configuration
(see Figure \ref{fig:antpos})
at the Karoo Radio Observatory site in South Africa.
A 100-MHz band from 100-200MHz was correlated
with 2048 frequency channels and integrated for 10.7 seconds before
visibilities were stored.  Observations included here on  July 4, 2011, running
from JD2455748.17 to JD2455748.72. and October 17, 2011 running from
JD2455852.2 to JD2455852.6.  In both seasons two antennas were omitted owing to
malfunctioning signal path. This 20 hour long combined dataset provides
observations provides complete hour angle coverage for the entire 24 hours of
Right Ascension. The July portion of the dataset comes from the same observing
campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
%July (\#40,\#55), September (\#7,\#28)

% XXX incorporate
We use data observed on JD2455747 
from a 64-antenna single-polarization deployment of the 
PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
of these observations and their calibration are given in \citet{pober_et_al2013}.

@@

%CALIBRATION
\textbf{Per-Antenna Gain and Phase Calibration}\\

% XXX differentiate amp cal here from spectral cal and absolute cal that comes later.

% XXX time-dependent calibration is critical.  modify paragraph below
Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was drived using coefficients characterized in
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

Antenna delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013XXX} and \citet{Stefan:2013:XXX}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

% XXX incorporate
To measure the spectrum of each source, we begin by applying per-antenna phase and gain
calibrations established via self-calibration.  We next remove
the known dependence of amplifier gain and cable attenuation on ambient temperature 
using measured temperature data and temperature coefficients that were characterized in
laboratory measurements \citep{parashare_bradley2009} and confirmed 
in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
osition
and sum over 
all baselines greater than 20 wavelengths in length.
A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
is applied to the resulting
beam to suppress beam sidelobes where sources introduce variations that deviate more than 
$\pm$0.1 mHz from the fringe rate of the source in question.

%BEAMFORMING,FILTERING, AVERAGING

@@

% XXX specific discussion of baseline weights to compensate for resolution effects for Pictor A
% XXX need to elaborate on correcting for resolution effects for PicA.
% XXX check paragraph below for relavant phrases
Because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.

@@

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
% XXX clarify why one source used here, and more sources later 
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

@@

To compare with observations at other frequencies we must assume a spectral
model. The prevailing spectral model for low frequency radio sources is a
single power law due to synchrotron emission, though curvature or other
deviation from a power-law is not-uncommon.   To establish a baseline model, we
fit a spectral model to prior catalog data from the spectrally and spatially
cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method
described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for
these fits are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}, and
illustrated in Figure \ref{fig:src_spec}.

@@

The data  include new measurements of Pictor A that are uncertain to 3.5\%,
close to the level of the most precise higher frequency measurements by
\citet{Wills:1975p9314}. Using these new measurements we update the spectral
calibration model to an accuracy of 2.5\%. As validation of this method, we
also measure a selection of 58 additional sources at the same Declination.
